---
title: "Creating COVID19 planning scenario reports"
author: "Joshua Kaminsky"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

# Introduction

The purpose of htis document is to provide full instruction on how to create a report using the COVIDScenarioPipeline.

## Scope

The report you will create discusses planning scenarios for different interventions on COVID19.  This is not a forecasting pipeline, and I will provide no explanation about how it may transfer to another disease.

#### Specific Limitations

 %% POPULATE ME please help scientists

 - Interventions need to be implemented as an effect on `beta`.  Some more mechanistic interventions cannot easily be captured this way.

# Overview

The pipeline is broken into several stages, each of which can be independently replaced.

### Pipeline Phases

#### Seeding

We run a model to determine the likelihood of importing cases into the region of interest.  We maintain an [R package](https://github.com/HopkinsIDD/covidImportation).



#### Epidemic Simulation

We run a location stratified [SEIR model](https://github.com/HopkinsIDD/COVIDScenarioPipeline/tree/dataseed/SEIR), using a python module in `COVIDScenarioPipeline`.

#### Hospitalization Estimation

We estimate secondary effects of infection using infection numbers using the [hospitalization](https://github.com/HopkinsIDD/COVIDScenarioPipeline/tree/dataseed/R/pkgs/hospitalization) R package in `COVIDScenarioPipeline`.

#### Report Generation

We provide functions to access results and help produce reports in the [report_generation](https://github.com/HopkinsIDD/COVIDScenarioPipeline/tree/dataseed/R/pkgs/report_generation) R package in `COVIDScenarioPipeline`.

### Pipeline Configuration

#### config.yml

Most of the configuration done for this package is set in this configuration file.  A default is provided, but you should feel free to make your own copy tailored to your needs.

# Getting Set up

This project uses R, python, pandoc, and make

#### R

The code requires R version 3.6 or newer. You can download R from [cran](https://cran.rstudio.com/).  We also recommend [rstudio](https://rstudio.com/products/rstudio/download/), an R IDE.  We keep a list of [R packages](https://github.com/HopkinsIDD/COVIDScenarioPipeline/blob/dataseed/packages.R).  You can source the script to install the versions required (the most recent versions also likely work).

#### python

We use python3.6 or newer.  There is a python package we use that needs to know about R, so ensure you install R before python. This differs based on operating system. We keep a list of [python modules](https://github.com/HopkinsIDD/COVIDScenarioPipeline/blob/dataseed/requirements.txt).

##### Windows

My preference here has been to use windows subsystem for linux (WSL), and use the linux instructions.

You can find installation instructions [here](https://docs.microsoft.com/en-us/windows/wsl/install-win10)

If you want to try something else, you can [directly download](https://www.python.org/downloads/release/python-382/) python.  During installation, be sure to add it to your path, or make won't work.

##### Linux (Debian)

```
# apt install python3 python3-pip
```

##### Mac

%% POPULATE ME - can someone who has a mac make sure this works?

[This webpage](https://docs.python-guide.org/starting/install3/osx/) has a guide to installing python3 and pip on mac

### pandoc

Pandoc is part of R markdown, but needs to be installed separately.  You can download it [here](https://github.com/jgm/pandoc/releases/tag/2.9.2)

### make

Make should already come with your system

# Seeding

The code for this section is in an [R package](https://github.com/HopkinsIDD/covidImportation).

Calculate the expected number of cases imported from outside of the region of interest.

# Epidemic Simulation

The code for this section is in the [SEIR](https://github.com/HopkinsIDD/COVIDScenarioPipeline/tree/dataseed/SEIR) python module in `COVIDScenarioPipeline`.

We have code for a SEIR compartmental model with three infectious states.
Within each geographic location, we assume even mixing.
Between locations, we have a movement model based on empirical data you will need to provide.

## SEIR parameters
The epidemic is controlled by sigma, gamma, and R0

## Geographic Data

This file contains the geographic information over which the simulation should be run.
It should have one line per location, and at least two columns containing information about those locations:
- `geoid` A column containing a unique identifier for the location
- `popnodes` A column containing the population of that location

## Mobility File

A matrix (stored as a space delimited scientific notation e.g., 0.000000000000000000e+00).  The matrix is used to calculate movement rates between geoids.  The number of people who move from `source` to `dest` is binomially distributed with probability `1 - exp( - mobility[source,dest] / popnodes[source] * dt)`

## Filter

A matrix (number of days simulated x number of geographic nodes).  Each value contains a minimum number of cases for that time and place.  The SEIR simulation throws out simulations that are inconsistent with these reports.

Currently, the filter is strict, meaning that any simulation that doesn't pass it exactly is rejected.  We expect to provide a more relaxed version that provides a tolerance parameter.

## Seeding or importation

in the `config.yaml` file:

```
seeding:
  method: FolderDraw
  folder_path: model_output/importation/
# OR !
seeding:
  method: PoissonDistributed
  lambda_file: data/west-coast-AZ-NV/seeding.csv
```


`FolderDraw`: each sim will pull importation from file `importation_{$UID}.csv` in folder `folder_path`. If there is more sims than files in this folder, it’ll loop. `$UID` starts 1 to match R 1-based indexing.
`PoissonDistributed`: will draw a poisson with lambda specified in à `lambda_file`

In both methods, csv files needs to have at least three columns named `place,date,amount` . `place` are places that match exactly a `place` in the `geodata.csv`. `date` are cases dates in any sensible format, and `amount` either the number of importation (`FolderDraw`) or the lambda parameter of the poisson (`PoissonDistributed`).

in the CA repo, in `data/west-coast-AZ-NV/seeding.csv` there is an example file. I created it taking cum cases until the model start date, multiplied by 5 and adding 0.1 (so there is a chance in every county). This is a good way to start if the importation module is not availble for you.



## Interventions

In order to allow flexibility in  interventions, we currently use an R script to define an intervention.  We provide several exampes in the NPI folder. In the future, we expect to move away from this model and toward specifying interventions directly in the config files.

To write an intervention, you need to write an R script that creates a matrix of your intervention's effects on `beta` by providing `NPI`, a matrix of percentage reduction for each location and time.  To reduce beta by 20% deterministically, one could use

```{r, eval=FALSE}
## This block sets default values so the NPI can be tested outside of python
if (!from_python) {         # or whatever values you use to test.
    ti_str <- '2020-01-31'
    tf_str <- '2020-08-31'
    foldername <- 'west-coast/'
}

## This pulls data to determine the size of the location x time matrix
county.status <- read.csv(paste0(foldername,'geodata.csv'))
dates <- seq.Date(as.Date(ti_str), as.Date(tf_str), 1)

## This creates and sets the location x time matrix.
NPI <- as.data.frame(matrix(0.2, dim(county.status)[1],length(dates)), dimnames = list()
```

# Hospitalization and Outcome Generation

The code for this section is in the [hospitalization](https://github.com/HopkinsIDD/COVIDScenarioPipeline/tree/dataseed/R/pkgs/hospitalization).
After you have run a simulation, and have infection rates, we use those results to calculate hospitalizations, icu admittances, ventilator use, deaths (and it would be relatively easy to add other outcomes if you have data).

### Probability Parameters

There are currently 5 variables that we measure track.  Infection (I), Hospitalization (H), death (D), ICU admittance (ICU), and Ventilator use (Vent).  They are calculated from eachother starting from infection, which we get from the Epidemic simulation.  Each parameter has an associated probability (p_H, p_D, etc.) which represents that probability of that event conditional on another event.  The dependence of the parameters is summarized by the following flowchart


The current flow looks like this:

```{r,echo=FALSE}

DiagrammeR::grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']

      # edge definitions with the node IDs
      tab1 -> tab2 [label = 'p_hosp'];
      tab2 -> tab3 [label = 'p_death'];
      tab2 -> tab4 [label = 'p_ICU'];
      tab4 -> tab5 [label = 'p_vent'];
      }

      [1]: 'Infection'
      [2]: 'Hospitalization'
      [3]: 'Death'
      [4]: 'ICU'
      [5]: 'Ventilation'
      ")
```

### Duration Parameters

For each event that has a probability, there is an associated time parameter, which measures expected time before that event from infection.  The parameter is given as two numbers, and the expectation is calculated as `round(exp(time_X_pars[1] + X_pars[2]^2 / 2))`.

%% POPULATE ME - Need explanation for why the parameters are of the above form

There are two other parameters that calculate different amounts of time.  They are in the same form, but measure the duration of one of the above events.  time_ICUdur_pars, and time_dischdur_pars measure the length of ICU stay and hospital stay respectively.

# Report Generation

We provide a [package](https://github.com/HopkinsIDD/COVIDScenarioPipeline/tree/dataseed/R/pkgs/report_generation) to help utilize the previous parts of the pipeline to create meaningful reports.  This support comes in the form of functions to help load the output of previous steps (it is sometimes quite large), and R Markdown templates to allow the easy creation of customizable reports without requiring the user to start from scratch.

## Functions

We provide two functions to load the results from the [Epidemic Simulation] and [Hospitalization and Outcome Generation], `load_scenario_sims_filtered` and `load_hosp_sims_filtered` respectively.  These functions perform the same function on the two different data sources.  Because of the nature of the data, they do have different syntax though

#### load_scenario_sims_filtered

```{r, eval = FALSE}
load_scenario_sims_filtered <- function(
  scenario_dir,
  post_process=function(x) {x},
  pre_process=function(x){x}
)
```

 - `scenario_dir` is the directory containing the output of the [Epidemic Simulation].  The function assumes it is in the `model_output` subdirectory of this directory.  You can access this by  %POPULATE ME - how to use
 - `pre_process` is a function to be performed on each simulation file before transforming into a long data frame.
 - `post_process` A function to be performed on each simulation file after transforming into a long data frame.

#### load_hosp_sims_filtered

```{r, eval = FALSE}
load_hosp_sims_filtered <- function(
  scenario_dir,
  name_filter=function(x) {x},
  post_process=function(x){x}
)
```

 - `scenario_dir` is the directory containing the output of the [Hospitalization and Outcome Generation].  The function assumes it is in the `hospitalization/model_output` subdirectory of this directory.  You can access this by %POPULATE ME - how to use
 - `post_process` A function to be performed on each simulation file after each piece of data is loaded.
 - `name_filter` A string that all filenames need to match.  This is intended for distinguishing between different hospitalization parameterization scenarios, which are stored with the scenario as part of the filename.

## Templates

We have generated templates to help create reports of different types.  Templates are complete reports that you can use as a base of your output.  Currently, we have the beginning of one template intended for state level reports.

#### Using templates

To start a draft from a template, you can use, for example:

```{r, eval = FALSE}
rmarkdown::draft("Maryland_Report.Rmd", template = "state_report", package = "report_generation")
```


# Appendixes

### Implemented interventions

Each intervention is associated with a start and end date and a range of values to sample from.

### None

This is a non-intervention scenario. It does not reduce `R0`.
```{r None}
None:
      template: ReduceR0
      period_start_date: YYYY-MM-DD
      period_end_date: YYYY-MM-DD   
      value:
        distribution: fixed
        value: 0
```

### SchoolClosure

This intervention represents school closures. It reduces `R0` by 16-30%.

```{r School Closure}
SchoolClosure:
      template: ReduceR0
      period_start_date: YYYY-MM-DD
      period_end_date: YYYY-MM-DD
      value:
        distribution: truncnorm
        a: 0.16
        b: 0.30
        mean: 0.18
        sd: 0.05
```



### Influenza1918

This intervention represents the influence of different social distancing scenarios observed in the 1918 Influenza. It reduces `R0` by 44-65%, based on values observed in Milwaukee, Wisconsin. These values can be altered to reflect different cities and scenarios reported by M.Bootsma & N.M.Ferguson in https://www.pnas.org/content/104/18/7588.long

```{r Influenza1918}
Influenza1918:
      template: ReduceR0
      period_start_date: YYYY-MM-DD
      period_end_date: YYYY-MM-DD
      value:
        distribution: uniform
        low: .44
        high: .65
```

### Wuhan

This intervention represents shelter in place similar to what was done in Wuhan at the beginning of the outbreak. It reduces `R0` by 81-89%.

```{r Wuhan}
Wuhan:
      template: ReduceR0
      period_start_date: YYYY-MM-DD
      period_end_date: YYYY-MM-DD
      value:
        distribution: uniform
        low: .81
        high: .89
```

### TestIsolate

This intervention represents rapid testing and isolation of cases, similar to what was done in Wuhan at the beginning of the outbreak. It reduces `R0` by 45-96%.

```{r TestIsolate}
TestIsolate:
      template: ReduceR0
      period_start_date: YYYY-MM-DD
      period_end_date: YYYY-MM-DD
      value:
        distribution: uniform
        low: .45
        high: .96
```

### Mild

This intervention has two sequential interventions: School closures followed by a Wuhan-style lockdown.

```{r Mild}
Mild:
    template: Stacked
    scenarios:
      - SchoolClosure
      - Wuhan
```
### Mid

This intervention has three sequential interventions: School closures, followed by a Wuhan-style lockdown, followed by social distancing practices used during the 1918 Influenza pandemic.

```{r Mid}
Mid:
    template: Stacked
    scenarios:
      - SchoolClosure
      - Wuhan
      - Influenza1918
```

### Severe

This intervention has three sequential interventions: School closures, followed by a Wuhan-style lockdown, followed by rapid testing and isolation.

```{r Severe}
Severe:
    template: Stacked
    scenarios:
      - SchoolClosure
      - Wuhan
      - TestIsolate
```


## Actual Steps I went through to create a minimal working repository (by commit)


 - Install python packages

   ```{sh, eval=FALSE}
   pip3 install -r https://raw.githubusercontent.com/HopkinsIDD/COVIDScenarioPipeline/dataseed/requirements.txt
   ```

 - Install cran R dependencies

   ```{r,eval=FALSE,echo=TRUE}
   source_url("https://raw.github.com/lcolladotor/ballgownR-devel/master/ballgownR/R/infoGene.R")
   ```

 - Install all relevant R packages from github:

   ```{r,eval=FALSE,echo=TRUE}
   devtools::install_github(repo='HopkinsIDD/COVIDScenarioPipeline', ref='dataseed', subdir='R/pkgs/covidcommon')
   devtools::install_github(repo='HopkinsIDD/COVIDScenarioPipeline', ref='dataseed', subdir='R/pkgs/hospitalization')
   devtools::install_github(repo='HopkinsIDD/COVIDScenarioPipeline', ref='dataseed', subdir='R/pkgs/report_generation')
   ```

 - Clone github repo
   ```{sh, eval=FALSE}
   git clone https://github.com/HopkinsIDD/COVIDScenarioPipeline.git
   ```

 - Copy the config.yml file from the COVIDScenarioPipeline repository to your current repository
   ```{sh, eval=FALSE}
   cp COVIDScenarioPipeline/config.yml config.yml
   ```

 - Remove all references to the COVIDScenarioPipeline repo from config.yml

   ```{eval=FALSE}
   1c1
   < name: mid-west-coast-AZ-NV
   ---
   > name: minimal
   5c5
   < dynfilter_path: data/west-coast-AZ-NV/filtergithub.txt
   ---
   > dynfilter_path: data/filtergithub.txt
   8c8
   <   base_path: data/west-coast-AZ-NV
   ---
   >   base_path: data
   10c10
   <   setup_name: west-coast-AZ-NV
   ---
   >   setup_name: minimal
   16c16
   <   scripts_path: COVIDScenarioPipeline/NPI
   ---
   >   scripts_path: NPI
   ```

 - Make an Intervention

   ```{sh, eval=FALSE}
   mkdir NPI
   cp COVIDScenarioPipeline/NPI/None.R NPI/
   ```

 - Aquire geodata

   ```{sh, eval=FALSE}
   mkdir data
   echo "geoind,population
10001,1000
20002,2000" > data/geodata.csv
   ```
   Edit the config file so spatial_setup::base_path = data
   Edit the config file so spatial_setup::geodata = geodata.csv

 - Aquire mobility data

   ```{sh, eval = FALSE}
   echo "0 .03
.03 0" > data/mobility.txt
   ```
   Edit the config file so spatial_setup::mobility = mobility.csv
   Note that geodata and mobility data live in the same directory (basepath)

 - Aquire filter

   ```{sh, eval=FALSE}
   echo "0 0" > data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   echo "0 0" >> data/filter.txt
   ```
   The number of columns should be the number of geoids
   The number of time steps should be end_date - start_date in days
   dynfilter_path should be a path to this file

 - Run simulate.py

   ```{sh, eval=FALSE}
   simulate.py -c config.yml -s None -n 15
   ```

 -
