---
title: "Sanity Check and Data Compare"
output: 
  html_document: 
    theme: journal
    fig_caption: true
params: 
  config_file: config_inference_ca_counties_med_forecast.yml # add sanity: with run ("country" or "state"), country (e.g. "US"),  state (if run=="state"), and inference (T/F)
  runs_folder: runs_20200817 # folder name with output folders hosp, hpar, snpi, spar
  pi_lo: 0.05
  pi_hi: 0.95
  hosp_eval: FALSE # do we want to compare with hospitalization data? currently only enabled for CA 
---

```{r setup, include=FALSE}
library(covidcommon)
library(report.generation)
library(tidyverse)
library(cdlTools)
library(doParallel)

knitr::opts_chunk$set(
    echo = FALSE,
    fig.align = "center",
    message = FALSE,
    warning = FALSE,
    cache.lazy = FALSE,
    bitmapType = "cairo"
    )

# Setting output/root directories by running "R -e "rmarkdown::render()"" from terminal 
#Option 1: root.dir is set to the folder with the config, BUT only works if CSP is a subdirectory of COVID19_Location. output_dir = getwd() in render

knitr::opts_knit$set(eval.after = 'fig.cap',
                     root.dir = rprojroot::find_root(rprojroot::has_file(params$config_file))) # searches for root directory with config file (if csp is subdir)

#Option 2 (more flexible): set output.dir to getwd() and knit_root_dir to a specific folder in rmarkdown::render. However, opts_knit$set cannot have an root.dir argument (it did not work for me)
#
 # knitr::opts_knit$set(eval.after='fig.cap')

options(scipen=999)
```

```{r load_config}
config <- covidcommon::load_config(params$config_file)

geodata <- load_geodata_file(file.path(config$spatial_setup$base_path, config$spatial_setup$geodata),
                             geoid_len=5)
```

```{r setup_config_vals}
# Config must have (alternatively could pull from other sections of config/set params)
#     run: country or state
#     country: US (other not yet suppported)
#     pdeath_levels: ['high', 'med', 'low'] 
#     state: CA     (if run==country)   
#     npi_trimmer:"[[A-Z]]+\\_"       pattern for str_remove to trim intervention names down to common groups. ONLY IF INTERVENTIONS VARY BY GEOID OVER TIME 
#     Config may have:
#     fit_date: "2020-06-23" # serves as cut-off date for comparison of model estimates vs reported data 
#     

run <- as.character(config$sanity$run) # either state, states/region or country
country<-config$sanity$country
pdeath_levels <- config$sanity$pdeath_levels
infer <- exists("filtering", where = config) ## is there inference in the runs?
npi_trimmer<- config$sanity$npi_trimmer
current_scn <- config$interventions$scenarios[1]

if(is.null(config$sanity$fit_date)){
  fit_date<-lubridate::ymd(Sys.Date()-1)
} else {
  fit_date<-lubridate::ymd(config$sanity$fit_date)
}
geogroup <- case_when(run=="state" ~ "geoid", # Determine whether grouping is done for counties (in state runs) or states (in country runs)
                      run=="country" ~ "USPS")

affected_geoids <- lapply(config$interventions$settings, 
                          exists, x="affected_geoids") %>% # interventions different across geoids?
  unlist(use.names=FALSE) %>% 
  any()
        
```

```{r infer_params, eval=infer}
npi_names<- names(config$interventions$settings[unlist(lapply(config$interventions$settings, exists, x="perturbation"))]) # names of periods with inference 
npi_label <- NA

```

```{r formatting}
geo_names <- tigris::fips_codes %>%
  filter(state %in% {if(run=="state") config$sanity$state else(c(config$spatial_setup$modeled_states))})%>%
  unite(col="geoid", ends_with("_code"), sep="") %>%
  dplyr::select(geoid, name=county, USPS=state) %>%
  mutate(name=str_remove(name, " County"),
         geoid=case_when(str_detect(geoid, "^72") ~ "72000",
                         str_detect(geoid, "^66") ~ "66000",
                         str_detect(geoid, "^69") ~ "69000",
                         str_detect(geoid, "^78") ~ "78000",
                         TRUE ~ geoid)) %>%
  {if(run=="country") distinct(.,geoid, USPS) else(.)}%>%
  filter(geoid %in% geodata$geoid) 

included_geoids <- geo_names$geoid 

geo_names <- geo_names %>%
  {if(run=="state")
    mutate(., name=factor(name, levels=sort(unique(geo_names$name), decreasing=TRUE)))
    else(mutate(., USPS=factor(USPS, levels=sort(unique(geo_names$USPS), decreasing=TRUE))))}


fig_counter<-1
tab_counter<-1
```


## Summarize Run Parameters  

`r paste0("**Tab.", tab_counter, "**: Summary of config SEIR parameters")`

```{r param_summary}

seir <- config$seir$parameters

seir <- tibble(value = unlist(seir), names = names(unlist(seir))) %>%
    separate(names, into = c("names", "val"), sep = "\\.") %>%
    dplyr::select(names, val, value) %>%
    unite(value, val:value, sep=": ", na.rm=TRUE) %>%
    group_by(names) %>%
    summarise_all(funs(paste0(.,collapse='\n'))) %>%
    right_join(seir%>%names()%>%tibble(names=.)) %>%
    mutate(section= "SEIR") 

seir%>%
    dplyr::select(Section = section, Parameters = names, Value = value) %>%
    flextable::flextable() %>%
    flextable::merge_v(j="Section") %>%
    flextable::autofit() %>%
    flextable::theme_vanilla()

tab_counter <- tab_counter+1
```


`r paste0("**Tab.", tab_counter, "**: Summary of outcome parameters (from hpar)")`

```{r}

hpar<- load_hpar_sims_filtered(params$runs_folder,
                               incl_geoids = included_geoids) 

hpar<-hpar%>%
  filter(scenario == unique(hpar$scenario)[1])

hpar%>%
  {if(run=="state") right_join(.,geo_names)
    else(left_join(.,geo_names))} %>%
  # {if(run=="state") filter(., geoid %in% geo_names$geoid) 
  #   else(filter(., USPS %in% geo_names$USPS))} %>%
    mutate(pdeath=factor(pdeath, levels=pdeath_levels))%>%
    group_by(outcome, pdeath)%>%
    summarize(value_lo=quantile(value,params$pi_lo, na.rm=TRUE),
              value_hi=quantile(value,params$pi_hi, na.rm=TRUE),
              value=mean(value, na.rm=TRUE)) %>%
    dplyr::select(outcome, pdeath, value, value_lo, value_hi) %>%
    mutate_if(is.numeric, function(x) round(x*100,2))%>%
    mutate(value_hi=str_replace(value_hi, '$', '\\)'),
           value_lo=str_replace(value_lo, '^', '\\(')) %>%
    unite(col=ci, value_lo:value_hi, sep="-") %>%
    flextable::flextable()%>%
    flextable::autofit()%>%
    flextable::set_header_labels(outcome="Outcome", pdeath="IFR", value="Probability", ci=paste0((params$pi_hi-params$pi_lo)*100, "% PI")) %>%
    flextable::merge_v(j=1) %>%
    flextable::theme_vanilla()
```

```{r, fig.cap=cap, fig.width=10, fig.height=10}

hpar%>%
  {if(run=="state") right_join(.,geo_names)
    else(left_join(.,geo_names))} %>%
    group_by(outcome, pdeath, !!as.symbol(geogroup))%>%
    summarize(value_lo=quantile(value,params$pi_lo),
              value_hi=quantile(value,params$pi_hi),
              value=mean(value)) %>%
    {if(run=="state") left_join(., geo_names)
        else(rename(., name=USPS))} %>%
    mutate(pdeath=factor(pdeath, levels=pdeath_levels)) %>%
    ggplot(aes(x=value, y=name, col=outcome)) +
    geom_point(position=position_dodge(0.75))+
    geom_linerange(aes(xmin=value_lo, xmax=value_hi), position=position_dodge(0.75),alpha=0.6)+
    facet_wrap(~pdeath)+
    theme_bw()+
    scale_x_sqrt() +
  theme(strip.text=element_text(face="bold", size=10))+
  ylab({if(run=="state")"County" else("State")}) 

cap<-paste0("**Fig.", fig_counter, "** Outcome values (hpar) by ", {if(run=="state") "county." else("state.")})
remove(hpar)
fig_counter<-fig_counter+1
```
  
```{r r_load, eval=infer}
#if run==country, then state_r0 is equivalent country_r0 and county_r0 is equivalent to state_r0
inference_r <- load_r_sims_filtered(params$runs_folder, 
                                    incl_geoids=included_geoids,
                                    npi_trimmer = npi_trimmer)

inference_r <- inference_r %>%
  filter(scenario==unique(inference_r$scenario)[1])

inference_r <- inference_r %>%
  group_by(!!as.symbol(geogroup), npi_name) %>%
  summarize(rq1 = quantile(r, 0.25, na.rm=TRUE), 
            rq3 = quantile(r, 0.75, na.rm=TRUE),
            r = mean(r, na.rm=TRUE), 
            reduc = mean(reduction, na.rm=TRUE), 
            reducq1 = quantile(reduction, 0.25, na.rm=TRUE), 
            reducq3 = quantile(reduction, 0.75, na.rm=TRUE)) %>%
  {if(affected_geoids) mutate(., npi_name=str_remove(npi_name, npi_trimmer))
    else(.)} %>%
  left_join(geo_names)
  
if(affected_geoids){
  npi_names<-npi_names%>%
    str_remove(npi_trimmer) %>%
    unique()
}
```

```{r reproductive_num, fig.height = 10, eval=infer, fig.cap=cap}
# if run==country, then state Rt is the mean Rt (each county weighted equally)
# 
cap<-paste0("**Fig.", fig_counter, "**: Estimated reproduction number at baseline and during previous interventions")

plot_r_num <- function(inference_dat, 
                       npiselection = npi_names,
                       npilabel = npi_label, 
                       periodcolors = c("chartreuse3", "brown2", "turquoise4", "black", "magenta3", "grey", "green", "goldenrod3", "red", "orange"),
                       distribution_low = NA, # if you want to show the assumed distribution for a particular intervention only then specify values/colors 
                        distribution_high = NA, 
                        distribution_colors = NA,
                       effectiveness=FALSE){
  
  if(!is.na(npilabel)){
    label <- tibble(npi_label = npilabel,
                    npi_name = npiselection)
  } else {
    label <- tibble(npi_label = npiselection,
                    npi_name = npiselection)
  }

  plot_r <- inference_dat %>%
    filter(npi_name %in% npiselection) %>%
    left_join(label) %>%
    mutate(npi_label = factor(npi_label, levels=label$npi_label))
  
  if(length(periodcolors)<length(npiselection)){
    stop(paste0("Specify additional colors. Current colors are: ", paste(periodcolors, collapse=", ")))
  }

  periodcolors <- periodcolors[npi_names %in% npiselection]
    
  if(effectiveness==TRUE){
  rc<-plot_r %>%
      ggplot(aes(x=reduc, y={if(run=="state") name else(USPS)}, col = npi_label)) +
      geom_point(position = position_dodge(0.75)) + 
      geom_linerange(aes(xmin=reducq1, xmax=reducq3, col = npi_label), 
                     position = position_dodge(0.75)) + 
      scale_color_manual(breaks = c(label$npi_label), 
                         values = periodcolors) +
      theme_bw() +
      theme(panel.grid.minor = element_blank(),
            legend.position = "bottom",
            legend.title = element_blank()) +
      scale_x_continuous(expand = c(0,0)) +
      coord_cartesian(xlim = c(0, 1.01)) +
      ylab({if(run=="state")"County" else("State")}) +
      xlab("Estimated intervention effect (mean and IQR)") +
      guides(color=guide_legend(nrow=2,byrow=TRUE))
    
  } else {
    rc <- plot_r %>%
    ggplot(aes(x=r, y={if(run=="state") name else(USPS)}, col=npi_label)) + 
    geom_point(position=position_dodge(1)) + 
    scale_color_manual(values = periodcolors)+
    geom_linerange(aes(xmin=rq1, xmax=rq3, col=npi_label), position=position_dodge(1)) +
    theme_bw() +
    theme(panel.grid.minor=element_blank(),
          legend.position = "bottom",
          legend.title = element_blank()) +
    scale_x_continuous(expand = c(0,0)) +
    coord_cartesian(xlim = c(0, 5)) +
    ylab({if(run=="state")"County" else("State")}) +
    xlab("Estimated reproductive number (mean and IQR)")+
    guides(color=guide_legend(nrow=2,byrow=TRUE))

  }

  if(!is.na(distribution_low)){
    for(i in 1:length( distribution_low)){
      rc <- rc + 
        annotate("rect", xmin= distribution_low[i], xmax= distribution_high[i], ymin=-Inf, ymax=Inf,
                 fill= distribution_colors[i], alpha=0.1)
    }
  }

return(rc)
}

plot_r_num(inference_r,
           npiselection=npi_names, 
           npilabel=npi_label)

fig_counter <- fig_counter+1 
```

```{r effectiveness, fig.height = 10, eval=infer, fig.cap=cap}
plot_r_num(inference_r, 
          npiselection=npi_names[-1],
          effectiveness=TRUE, 
          # distribution_low=0.2,#if you want to show the assumed distribution for a particular intervention
          # distribution_high=0.9,
          # distribution_colors="black",
          npilabel=NA)

cap<- paste0("**Fig. ", fig_counter, "**: Estimated effectiveness of NPIs.") #Shaded area reflects range of parameter values explored for the [insert] period.

fig_counter <- fig_counter+1
```

## Comparisons with USA Facts

```{r truth_load, include = FALSE}

truth_dat <- get_USAFacts_data() %>%
  rename(geoid=FIPS, USPS=source, date=Update)%>%
  right_join(geo_names) %>%
  filter(date<fit_date) %>%
  group_by(date, !!as.symbol(geogroup))%>%
  dplyr::summarize(Confirmed = sum(Confirmed, na.rm = TRUE), 
                   Deaths = sum(Deaths, na.rm = TRUE),
                   incidI =sum(incidI, na.rm=TRUE),
                   incidDeath=sum(incidDeath, na.rm = TRUE)) %>%
  ungroup()

if(params$hosp_eval){#comparison of hospital occupancy is currently only for "state", will require manual setup
    chhs_dat <- read.csv("data/DPH/covid19data.csv") %>% # 
      dplyr::select(name = County.Name, 
                    date = Most.Recent.Date, 
                    hosp = COVID.19.Positive.Patients)
    
    truth_dat <- chhs_dat %>%
      left_join(geo_names) %>%
      mutate(date = as.Date(date, "%m/%d/%Y")) %>%
      filter(date<=fit_date) %>%
      tibble()%>%
      right_join(truth_dat) %>%
      arrange(date)
}


```

```{r model_res_load}

res_state<-list() # loop works for larger datasets (e.g. USA)
for(i in 1:length(pdeath_levels)){
  res_state[[i]] <- arrow::open_dataset(paste0(params$runs_folder,"/hosp/"),
                                partitioning = c("geoid", "scenario", "pdeath", "date", "lik_type", "is_final", "sim_id")) %>%
    filter(is_final=="final",
           lik_type=="global") %>%
    dplyr::select(time, geoid, scenario, pdeath, sim_id, incidD, incidC, incidH, incidI, hosp_curr)%>%
    filter(pdeath==pdeath_levels[i]) %>%
    filter(time<fit_date)%>%
    collect() %>%
    group_by(geoid, pdeath, sim_id, scenario) %>%
    mutate(cumDeaths=cumsum(incidD),
           cumHosp=cumsum(incidH),
           cumInf=cumsum(incidI),
           cumCase=cumsum(incidC)) %>%
    left_join(geo_names) %>%
    group_by(!!as.symbol(geogroup), sim_id, scenario, time, pdeath) %>%
    summarize(currHosp=sum(hosp_curr),
              incidD=sum(incidD),
              incidC=sum(incidC),
              cumDeaths=sum(cumDeaths),
              cumInf=sum(cumInf),
              cumHosp=sum(cumHosp),
              cumCase=sum(cumCase)) %>%
    group_by(!!as.symbol(geogroup), time, pdeath, scenario)%>%
    summarize(cumDeaths_5pct=quantile(cumDeaths,probs=params$pi_lo),
              cumDeaths_95pct=quantile(cumDeaths,probs=params$pi_hi),
              incidD_5pct=quantile(incidD,probs=params$pi_lo),
              incidD_95pct=quantile(incidD,probs=params$pi_hi),
              currHosp_5pct=quantile(currHosp, probs=params$pi_lo),
              currHosp_95pct=quantile(currHosp, probs=params$pi_hi),
              incidC_5pct=quantile(incidC,probs=params$pi_lo),
              incidC_95pct=quantile(incidC,probs=params$pi_hi),
              currHosp=mean(currHosp),
              cumDeaths=mean(cumDeaths),
              incidD=mean(incidD),
              incidC=mean(incidC),
              cumInf=mean(cumInf),
              cumHosp=mean(cumHosp),
              cumCase=mean(cumCase))%>%
  mutate(time=as.Date(time))

  if(i==length(pdeath_levels)){
    res_state<- bind_rows(res_state)%>%
      mutate(pdeath=factor(pdeath, levels=pdeath_levels))%>%
      {if(run=="state") left_join(., geo_names) %>% mutate(., name=factor(name, levels=levels(geo_names$name)))
        else(mutate(., USPS=factor(USPS, levels=levels(geo_names$USPS))))}
  }

}

res_state<-res_state%>%
  filter(scenario==unique(res_state$scenario)[1])
```

`r paste0("**Tab.", tab_counter, "**: Model fit metrics to USA Facts data")`
```{r mod_metrics, fig.cap=cap}

deaths<-res_state%>%
  group_by(pdeath, time)%>%
  dplyr::select(starts_with("cumDeaths")) %>%
  summarize_if(is.numeric,sum)%>%
  inner_join(truth_dat%>%
               group_by(time=date)%>%
               summarize_if(is.numeric, sum)) %>%
  mutate(error = abs(cumDeaths-Deaths),
         Deaths=Deaths+1,# To avoid pesky Inf/NaN
         cumDeaths=cumDeaths+1,
         cumDeaths_5pct=cumDeaths_5pct+1,
         cumDeaths_95pct=cumDeaths_95pct+1,
         relative = abs(cumDeaths-Deaths)/Deaths,
         within = if_else(Deaths>cumDeaths_95pct |
                            Deaths<cumDeaths_5pct, 0, 1)) %>%
  summarize(mae = round(sum(error, na.rm=TRUE)/n(),2),
            relative = round(sum(relative, na.rm=TRUE)/n(),3),
            within = round(sum(within, na.rm=TRUE)/n(),3)) %>%
  mutate(Comparison = "Estimated vs Reported Cumulative Deaths")


deaths_I <- res_state %>% 
  group_by(pdeath, week=lubridate::floor_date(time,unit="week", week_start=1))%>%
  dplyr::select(starts_with("incidD"))%>%
  summarize_if(is.numeric,sum)%>%
  inner_join(truth_dat%>%
               group_by(week=lubridate::floor_date(date,unit="week", week_start=1))%>%
               summarize_if(is.numeric, sum)) %>%
  mutate(error = abs(incidD-incidDeath),
         incidDeath=incidDeath+1,# To avoid pesky Inf/NaN
         incidD=incidD+1,
         incidD_5pct=incidD_5pct+1,
         incidD_95pct=incidD_95pct+1,
         relative = abs(incidD-incidDeath)/incidDeath,
         within = if_else(incidDeath>incidD_95pct |
                            incidDeath<incidD_5pct, 0, 1)) %>%
  summarize(mae = round(sum(error, na.rm=TRUE)/n(),2),
            relative = round(sum(relative, na.rm=TRUE)/n(),3),
            within = round(sum(within, na.rm=TRUE)/n(),3)) %>%
  mutate(Comparison = "Estimated vs Reported Incident Deaths")

infects<- res_state %>% 
  group_by(pdeath, week=lubridate::floor_date(time,unit="week", week_start=1))%>%
  dplyr::select(starts_with("incidC"))%>%
  summarize_if(is.numeric,sum)%>%
  inner_join(truth_dat%>%
               group_by(week=lubridate::floor_date(date,unit="week", week_start=1))%>%
               summarize_if(is.numeric, sum)) %>%
  mutate(error = abs(incidC-incidI),
         incidC=incidC+1, 
         incidI_conf=incidI+1,
         incidC_95pct=incidC_95pct+1,
         incidC_5pct=incidC_5pct+1,
         relative = abs(incidC-incidI)/incidI,
         within = if_else(incidI>incidC_95pct |
                            incidI<incidC_5pct, 0, 1)) %>%
  summarize(mae = round(sum(error)/n(),2),
            relative = round(sum(relative)/n(),3),
            within = round(sum(within)/n(),2)) %>%
  mutate(Comparison = "Estimated vs Reported Incident Cases (aggregated by week)")

if(params$hosp_eval){
hosp<- res_state%>% 
  group_by(pdeath, time) %>%
  dplyr::select(starts_with("currHosp"))%>%
  summarize_if(is.numeric, sum)%>%
  inner_join(truth_dat%>%
             group_by(time=date)%>%
             summarize_if(is.numeric, sum)) %>%
  mutate(error = abs(currHosp-hosp),
         hosp=hosp+1,
         currHosp=currHosp+1,
         currHosp_5pct=currHosp_5pct+1,
         currHosp_95pct=currHosp_95pct+1,
         relative = abs(currHosp-hosp)/hosp,
         within = if_else(hosp>currHosp_95pct |
                            hosp<currHosp_5pct, 0, 1)) %>%
  summarize(mae = round(sum(error)/n(),2),
            relative = round(sum(relative)/n(),3),
            within = round(sum(within)/n(),2)) %>%
  mutate(Comparison = "Estimated vs Reported Occupied Hospital Beds")}

{if(params$hosp_eval) bind_rows(deaths, deaths_I, hosp, infects) 
  else(bind_rows(deaths, deaths_I, infects))} %>%
  mutate(pdeath = str_to_title(pdeath)) %>%
  dplyr::select(Comparison, pdeath, mae, relative, within) %>%
  flextable::flextable()%>%
  flextable::set_header_labels(Comparison="Comparison", pdeath="Death Rate", mae="Mean Absolute Error", relative="Relative Absolute Error\n sum(abs(est-report)/report)/n()", within=paste0("Prop. of points within ", round((params$pi_hi-params$pi_lo)*100), "% PI")) %>%
  flextable::merge_v(j = "Comparison") %>%
  flextable::autofit() %>%
  flextable::theme_vanilla()

tab_counter<- tab_counter+1
  
```

## Check 1: Deaths vs. National/State Report  

```{r mdl_v_ob_death, fig.width=20, fig.height=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Modeled deaths vs. most recently reported deaths by death rate.")

map1<-res_state%>%
  filter(time==max(truth_dat$date))%>%
  inner_join(truth_dat%>%rename(time=date)) %>% 
  ggplot(aes(x=Deaths, y=cumDeaths, col=pdeath, label = {if(run=="state") name else(USPS)})) +
  ggrepel::geom_text_repel(segment.size = 0.2, alpha = 0.55) +
  geom_point() +
  scale_y_sqrt()+
  scale_x_sqrt()+
  geom_abline()+
  facet_wrap(~pdeath, nrow = 1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.text=element_text(face="bold", size=10))+
  scale_color_viridis_d(option = "viridis", begin = 0, end = 0.8) +
  xlab("observed deaths") +
  ylab("modeled deaths")

 map1 + coord_cartesian(xlim = c(0, max(map1$cumDeaths)*1.3))  

fig_counter <- fig_counter + 1  

``` 

```{r death_comp_bars, fig.height=10, fig.width=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Modeled vs most recently reported deaths by death rate and ", if_else(run=="country", "state.", "county."))

res_state%>%
  filter(time==max(truth_dat$date))%>%
  inner_join(truth_dat%>%rename(time=date)) %>%
  dplyr::select(time, !!as.symbol(geogroup), cumDeaths, Deaths, pdeath)%>%
  rename(observed=Deaths, modeled=cumDeaths)%>%
  pivot_longer(c(-time, -!!as.symbol(geogroup), -pdeath),
               names_to="source", values_to = "deaths") %>%
  {if(run=="state") left_join(.,geo_names) %>% mutate(., name=factor(name, levels=levels(geo_names$name))) 
    else(.)} %>%
  ggplot(aes(x= {if(run=="state") name else(!!as.symbol(geogroup))}, y=deaths, fill=source))+
  geom_bar(stat="identity",position=position_dodge()) +
  coord_flip() +
  scale_y_sqrt()+
  facet_wrap(~ pdeath) +
  xlab({if(run=="state") 'Counties' else('State')}) + 
  theme_bw()+
  theme(strip.text=element_text(face="bold", size=10))

fig_counter <- fig_counter+1
```

```{r heatmap_dat}

mapdat <-res_state%>%
  filter(time==max(truth_dat$date))%>%
  inner_join(truth_dat%>%rename(time=date)) %>%
  {if(run=="state") rename(., fips = geoid, full=name)  
    else (mutate(., full=cdlTools::fips(USPS, to="Name"), fips=cdlTools::fips(USPS, to="FIPS")))} %>%
  mutate(cfr_report=Deaths/Confirmed,
         cfr_model=cumDeaths/cumCase,
         Deaths=Deaths+1, # to avoid inf or NA
         cumDeaths=cumDeaths+1,
         death_ratio=cumDeaths/Deaths)%>%
  dplyr::select(fips,full, death_ratio, pdeath, cfr_report, cfr_model, Deaths, Confirmed, cumDeaths) 

if(country!="US"){
shp@data$id = rownames(shp@data)
shp.points = fortify(shp, region="id")

mapdat <- inner_join(shp.points, shp@data, by = "id") %>%
  {if(run=="state") mutate(., fips = as.character(GEOID))
    else(mutate(., full= case_when(STATEFP==10 ~ "Delaware",
                                    TRUE ~ cdlTools::fips(STATEFP, to="Name"))))} %>%
  full_join(mapdat) %>%
  filter(str_detect(group, ".1$")) 

for(i in 1:length((mapdat%>%filter(is.na(pdeath))%>%distinct(NAME))$NAME)){
 temp <- mapdat%>%
    filter(is.na(pdeath))
  
mapdat <- temp%>%
   mutate(pdeath="low") %>%
   bind_rows(mapdat)
mapdat <- temp%>%
   mutate(pdeath="med") %>%
   bind_rows(mapdat)
mapdat <- temp%>%
   mutate(pdeath="high") %>%
   bind_rows(mapdat)
}

mapdat<- mapdat%>%
  filter(!is.na(pdeath)) %>%
  mutate(pdeath=factor(pdeath, levels=pdeath_levels))
}
```

```{r death_comp_heatmap, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Ratio of estimated to most recently reported deaths", if_else(run=="country", " by state.", " by county."))

if(country=="US"){
  usmap::plot_usmap(data=mapdat, values="death_ratio", include=unique(geo_names$USPS))+
    scale_fill_gradient2(trans="log10",midpoint = 0, low="blue",high="red", limits=c(1/60,60),name="mod/obs")+
    facet_wrap(~pdeath, nrow=1)+
    theme(legend.position="bottom",
          strip.text=element_text(face="bold", size=10))
} else {
mapdat %>% 
  ggplot(aes(x=long, y= lat, group=group, fill=death_ratio)) + 
  geom_polygon() + 
  geom_path() +
  facet_wrap(~pdeath, nrow =1) +
  scale_fill_gradient2(trans="log10",midpoint = 0, low="blue",high="red", limits=c(1/60,60),name="mod/obs") +
  theme_void() +
  coord_fixed(1.5)+
    theme(strip.text=element_text(face="bold", size=10))
}

fig_counter <- fig_counter + 1
```

```{r observed_cfr, echo=FALSE, fig.cap=cap}
cap<- paste0("**Fig.", fig_counter, "**: Estimated and observed CFR from cumulative deaths and cases", if_else(run=="country", " by state.", " by county."))
## Look at ratio of cases to deaths to help think about possible biases in reporting
if(country=="US"){
  mapdat%>%
    pivot_longer(names_to="type",cols=c(cfr_report, cfr_model))%>%
    filter(type=="cfr_model" | (type=="cfr_report" & pdeath=="med")) %>%
    usmap::plot_usmap(data=., values="value", include=unique(geo_names$USPS))+
    scale_fill_gradient(name="CFR", low="#ffeda0",high="#f03b20") +
    facet_grid(type~pdeath)+
    theme(legend.position="bottom",
          strip.text=element_text(face="bold", size=10))

} else {
  mapdat %>% 
  pivot_longer(names_to="type",cols=c(cfr_report, cfr_model)) %>%
  filter(type=="cfr_model" | (type=="cfr_report" & pdeath=="med")) %>%
  ggplot(aes(x=long, y= lat, group=group, fill=value)) + 
  geom_polygon() + 
  geom_path() +
 facet_grid(type~pdeath)+
  scale_fill_gradient(name="CFR", low="#ffeda0",high="#f03b20") +
  theme_void() +
  coord_fixed(1.5)+
  theme(legend.position="bottom",
          strip.text=element_text(face="bold", size=10))
}

fig_counter <- fig_counter+1
```

```{r mdl_v_ob_ts, fig.width = 10, fig.cap=cap}

cap<-paste0("**Fig.", fig_counter, "**: Modeled vs reported deaths over time")

res_state%>%
  inner_join(truth_dat%>%rename(time=date))%>%
  group_by(pdeath,time)%>%
  dplyr::select(Deaths, starts_with("cumDeaths"))%>%
  summarize_if(is.numeric, sum)%>%
  ggplot(aes(x=time, y=cumDeaths, ymin=cumDeaths_5pct, ymax=cumDeaths_95pct)) +
  geom_line(col="red")+
  geom_ribbon(alpha=.1, fill = "red")+
  geom_point(aes(y=Deaths)) +
  facet_wrap(~pdeath, ncol=3)+
  scale_y_sqrt()+
  theme_bw()+
  ylab("deaths")+
  theme(strip.text=element_text(face="bold", size=10))

  fig_counter <- fig_counter+1
  

```

```{r, fig.height=10, fig.weight=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Mean absolute error for deaths", if_else(run=="country", " by state.", " by county."))

mae_deaths <- res_state %>%
    group_by(pdeath, !!as.symbol(geogroup)) %>%
    inner_join(truth_dat%>%rename(time=date)) %>%
    mutate(error = abs(cumDeaths-Deaths),
           cumDeaths = cumDeaths+1,
           Deaths=Deaths+1,
           cumDeaths_5pct=cumDeaths_5pct+1,
           cumDeaths_95pct=cumDeaths_95pct+1,
           Deaths = if_else(Deaths == 0, 1, Deaths),
           r_error = abs(cumDeaths-Deaths)/Deaths,
           within = if_else(Deaths>cumDeaths_95pct |
                            Deaths<cumDeaths_5pct, 0, 1)) %>%
    {if(run=="state") group_by(.,pdeath, !!as.symbol(geogroup), name) else(.)} %>%
    filter(!is.na(error)) %>%
    summarize(mae = sum(error, na.rm=TRUE)/n(),
              relative = sum(r_error, na.rm=TRUE)/n(),
              within = sum(within, na.rm=TRUE)/n())

mae_deaths %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=mae, y=group)) +
    geom_col()+
    facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
          strip.text=element_text(face="bold", size=10)
        ) +
  xlab("Mean absolute error for deaths") +
  scale_x_sqrt()

fig_counter <- fig_counter+1

```

```{r mae_deaths_r, fig.height=10, fig.weight=10, fig.cap=cap}
cap<- paste0("**Fig.", fig_counter, "**: Relative mean absolute error for deaths", if_else(run=="country", " by state", " by county "))

mae_deaths %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=relative, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7)) + 
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab("Relative mean absolute error for deaths") +
  coord_cartesian(xlim = c(0, max((filter(mae_deaths, !is.na(relative), relative!=Inf))$relative))) +
  scale_x_continuous(trans = "log1p", breaks = c(0, 0.25, 0.5, 1, 2, 4))+
    geom_vline(xintercept = 1, linetype="dashed")


fig_counter <- fig_counter+1

```

```{r within_deaths, fig.height=10, fig.weight=10, fig.cap=cap}

cap<-paste0("**Fig.", fig_counter, "**: Proportion of confirmed deaths outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval", if_else(run=="country", " by state.", " by county."), " Dashed line represents the overall mean.")

mae_deaths %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=1-within, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7)) +
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab(paste0("% of estimates outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval")) +
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0, 1.05))+
    geom_vline(xintercept = 1-(mae_deaths%>%ungroup()%>%summarize(m=mean(within)))$m, linetype="dashed")

fig_counter <- fig_counter+1

```

```{r, fig.height=10, fig.weight=10, fig.cap=cap}

cap<- paste0("**Fig.", fig_counter, "**: Modeled vs reported deaths over time in the four", {if(run=="state") " counties" else(" states")} ," with the largest MAE by death rate.")
## Comparison of cumulative curves by key states
key_group <- mae_deaths %>%
  group_by(pdeath) %>%
  top_n(4, mae) %>%
  mutate(mae = round(mae, 2)) %>%
  {if(run=="state") unite(., "group_mae", name:mae, sep=": ", remove = FALSE) else(unite(., group_mae, !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))}

res_state %>%
  left_join(key_group, by = c(geogroup, "pdeath")) %>%
  filter(!is.na(group_mae)) %>%
  group_by(pdeath,!!as.symbol(geogroup))%>%
  inner_join(truth_dat%>%rename(time=date), by = c("time", geogroup))%>%
  ggplot(aes(x=time, y=cumDeaths, ymin=cumDeaths_5pct, ymax=cumDeaths_95pct)) +
  geom_line(color = "red")+
  geom_ribbon(alpha=.1, fill = "red")+
  geom_point(aes(y=Deaths), col="black") +
  facet_wrap(~ pdeath+group_mae, nrow=3)+
  scale_y_sqrt() +
  theme_bw() + 
  theme(legend.position = "bottom") +
  ylab("deaths") +
  theme(axis.text.x = element_text(angle=45,hjust=1),
        strip.text=element_text(face="bold", size=10)
        )

fig_counter <- fig_counter+1
  
```

## Check 2: Incident Deaths  

```{r mdl_v_ob_ts_incidD, fig.width = 10, fig.cap=cap}

cap<-paste0("**Fig.", fig_counter, "**: Modeled vs reported incident deaths (aggregated by week) over time.")

res_state%>%
  inner_join(truth_dat%>%rename(time=date))%>%
  group_by(pdeath, time=lubridate::floor_date(time, unit="weeks"))%>%
  dplyr::select(starts_with("incidD")) %>%
  summarize_if(is.numeric, sum)%>%
  filter(time!=max(time))%>%
  ggplot(aes(x=time, y=incidD, ymin=incidD_5pct, ymax=incidD_95pct)) +
  geom_line(col="red")+
  geom_ribbon(alpha=.1, fill = "red")+
  geom_point(aes(y=incidDeath)) +
  facet_wrap(~pdeath, ncol=3)+
  scale_y_sqrt()+
  theme_bw()+
  ylab("deaths")

  fig_counter <- fig_counter+1
  

```

```{r, fig.height=10, fig.weight=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Mean absolute error for incident deaths (aggregated by week)", if_else(run=="country", " by state.", " by county."))

mae_deaths_i <- res_state %>%
  inner_join(truth_dat%>%rename(time=date)) %>%
  {if(run=="state") group_by(., pdeath, !!as.symbol(geogroup), time=lubridate::floor_date(time, unit="weeks"), name)
    else(group_by(., pdeath, !!as.symbol(geogroup), time=lubridate::floor_date(time, unit="weeks")))} %>%
  dplyr::select(starts_with("incidD")) %>%
  summarize_if(is.numeric, sum)%>%
  mutate(error = abs(incidD-incidDeath),
         incidD = incidD+1,
         incidDeath=incidDeath+1,
         incidD_5pct=incidD_5pct+1,
         incidD_95pct=incidD_95pct+1,
         incidDeath = if_else(incidDeath == 0, 1, incidDeath),
         r_error = abs(incidD-incidDeath)/incidDeath,
         within = if_else(incidDeath>incidD_95pct |
                          incidDeath<incidD_5pct, 0, 1)) %>%
  filter(!is.na(error)) %>%
  {if(run=="state") group_by(., pdeath, !!as.symbol(geogroup), name)
    else(group_by(.,pdeath, !!as.symbol(geogroup)))} %>%
  summarize(mae = sum(error, na.rm=TRUE)/n(),
            relative = sum(r_error, na.rm=TRUE)/n(),
            within = sum(within, na.rm=TRUE)/n())

mae_deaths_i %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=mae, y=group)) +
    geom_col()+
    facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
          strip.text=element_text(face="bold", size=10)
        ) +
  xlab("Mean absolute error for deaths") +
  scale_x_sqrt()

fig_counter <- fig_counter+1

```

```{r mae_deaths_i_r, fig.height=10, fig.weight=10, fig.cap=cap}
cap<- paste0("**Fig.", fig_counter, "**: Relative mean absolute error for incident deaths (aggregated by week)", if_else(run=="country", " by state", " by county "))

mae_deaths_i %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=relative, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7)) + 
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab("Relative mean absolute error for deaths") +
  coord_cartesian(xlim = c(0, max((filter(mae_deaths, !is.na(relative), relative!=Inf))$relative))) +
  scale_x_continuous(trans = "log1p", breaks = c(0, 0.25, 0.5, 1, 2, 4))+
    geom_vline(xintercept = 1, linetype="dashed")


fig_counter <- fig_counter+1

```

```{r within_deaths_i, fig.height=10, fig.weight=10, fig.cap=cap}

cap<-paste0("**Fig.", fig_counter, "**: Proportion of confirmed deaths (aggregated by week) outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval", if_else(run=="country", " by state.", " by county."), " Dashed line represents the overall mean.")

mae_deaths_i %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=1-within, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7)) +
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab(paste0("% of estimates outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval")) +
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0, 1.05))+
    geom_vline(xintercept = 1-(mae_deaths%>%ungroup()%>%summarize(m=mean(within)))$m, linetype="dashed")

fig_counter <- fig_counter+1

```

```{r, fig.height=10, fig.weight=10, fig.cap=cap}

cap<- paste0("**Fig.", fig_counter, "**: Modeled vs reported incident deaths (aggregated by week) over time in the four", {if(run=="state") " counties" else(" states")} ," with the largest MAE by death rate.")
## Comparison of cumulative curves by key states
key_group <- mae_deaths %>%
  group_by(pdeath) %>%
  top_n(4, mae) %>%
  mutate(mae = round(mae, 2)) %>%
  {if(run=="state") unite(., "group_mae", name:mae, sep=": ", remove = TRUE) else(unite(., group_mae, !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))}

res_state %>%
  left_join(key_group, by = c(geogroup, "pdeath")) %>%
  filter(!is.na(group_mae)) %>%
  inner_join(truth_dat%>%rename(time=date), by = c("time", geogroup))%>%
  group_by(pdeath, !!as.symbol(geogroup), time=lubridate::floor_date(time, unit="weeks"), group_mae)%>%
  dplyr::select(starts_with("incidD")) %>%
  summarize_if(is.numeric, sum)%>%
  group_by(pdeath,!!as.symbol(geogroup))%>%
  filter(time!=max(time))%>%
  ggplot(aes(x=time, y=incidD, ymin=incidD_5pct, ymax=incidD_95pct)) +
  geom_line(color = "red")+
  geom_ribbon(alpha=.1, fill = "red")+
  geom_point(aes(y=incidDeath), col="black") +
  facet_wrap(~ pdeath+group_mae, nrow=3)+
  scale_y_sqrt() +
  theme_bw() + 
  theme(legend.position = "bottom") +
  ylab("deaths") +
  theme(axis.text.x = element_text(angle=45,hjust=1)
        )

fig_counter <- fig_counter+1
  
```


`r ifelse(params$hosp_eval, "## Check 3: Estimated vs Reported Hospitalizations (CHHS Data)  ", '')`  

```{r mdl_v_ob_hosp, fig.width=20, fig.height=10, fig.cap=cap, eval=params$hosp_eval}
cap<-paste0("**Fig.", fig_counter, "**: Estimated versus reported occupied hospital beds on ", max(truth_dat$date))
  
res_state%>%filter(time==max(truth_dat$date))%>%
  inner_join(truth_dat%>%rename(time=date)) %>%
  {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
  ggplot(aes(x=hosp, y=currHosp, col=pdeath, label=group)) +
  ggrepel::geom_text_repel(segment.size = 0.2, alpha = 0.75, segment.alpha=0.5) +
  geom_point()+
  scale_y_sqrt()+
  scale_x_sqrt()+
  geom_abline()+
  facet_wrap(~pdeath, nrow=1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.text=element_text(face="bold", size=10)) +
  scale_color_viridis_d(option = "viridis", begin = 0, end = 0.8) +
  xlab(paste0("reported occupied hospital beds"))+
  ylab("modeled occupied hospital beds")
  
  fig_counter <- fig_counter+1

```

```{r mdl_v_ob_ts_hosp, fig.cap=cap, eval=params$hosp_eval} 
cap<-paste0("**Fig.", fig_counter, "**: Estimated vs reported occupied hospital beds over time by death rate")

res_state%>%
  inner_join(truth_dat%>%rename(time=date))%>%
  group_by(time, pdeath)%>%
  dplyr::select(starts_with("currHosp"), hosp) %>%
  summarize_if(is.numeric, sum)%>%
  ggplot(aes(x=time, y=currHosp, ymin=currHosp_5pct, ymax=currHosp_95pct)) +
  geom_line(color = "red")+
  geom_ribbon(alpha=.1,fill = "red")+
  geom_point(aes(y=hosp)) +
  facet_wrap(~pdeath, nrow=1)+
  theme_bw()+
  scale_y_sqrt()+
  ylab("occupied hospital beds")

fig_counter <- fig_counter+1
  
```

```{r, fig.height=10, fig.width=10, fig.cap=cap, eval=params$hosp_eval}

mae_hosp <- res_state %>%
    group_by(pdeath, !!as.symbol(geogroup)) %>%
    inner_join(truth_dat%>%rename(time=date)) %>%
    mutate(error = abs(currHosp-hosp),
           hosp=hosp+1,
           currHosp=currHosp+1,
           currHosp_5pct=currHosp_5pct+1,
           currHosp_95pct=currHosp_95pct+1,
           r_error = abs(currHosp-hosp)/hosp,
           within = if_else(hosp>currHosp_95pct |
                            hosp<currHosp_5pct, 0, 1)) %>%
    {if(run=="state") group_by(.,pdeath, !!as.symbol(geogroup), name) else(.)} %>%
    filter(!is.na(error)) %>%
    summarize(mae = sum(error, na.rm=TRUE)/n(),
              relative = sum(r_error, na.rm=TRUE)/n(),
              within = sum(within, na.rm=TRUE)/n())

mae_hosp %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=mae, y=group)) +
    geom_col()+
    facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
          strip.text=element_text(face="bold", size=10)
        ) +
  xlab("Mean absolute error for occupied hospital beds") +
  scale_x_sqrt()

```

```{r mae_hosp_r, fig.height=10, fig.weight=10, fig.cap=cap, eval=params$hosp_eval}
cap<- paste0("**Fig.", fig_counter, "**: Relative mean absolute error for occupied hospital beds", if_else(run=="country", " by state", " by county "))

mae_hosp %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=relative, y=group)) +
    #geom_col()+
    geom_point(aes(col=pdeath), position=position_dodge(0.7)) + 
    #facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab("Relative mean absolute error for occupied hospital beds") +
  coord_cartesian(xlim = c(0, max((filter(mae_hosp, !is.na(relative), relative!=Inf))$relative))) +
  scale_x_continuous(trans = "log1p", breaks = c(0, 0.25, 0.5, 1, 2, 4))+
    geom_vline(xintercept = 1, linetype="dashed")


fig_counter <- fig_counter+1

```

```{r within_hosp, fig.height=10, fig.weight=10, fig.cap=cap, eval=params$hosp_eval}

cap<-paste0("**Fig.", fig_counter, "**: Proportion of occupied hospital beds outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval", if_else(run=="country", " by state.", " by county."), " Dashed line represents the overall mean.")

mae_hosp %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=1-within, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7)) +
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab(paste0("% of estimates outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval")) +
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0, 1.05))+
    geom_vline(xintercept = 1-(mae_hosp%>%ungroup()%>%summarize(m=mean(within)))$m, linetype="dashed")

fig_counter <- fig_counter+1

```

```{r key_cum_hosp, fig.height=10, fig.wdith=10,fig.cap=cap, eval=params$hosp_eval}
cap<-paste0("**Fig.", fig_counter, "**: Estimated vs reported occupied hospital beds over time in the four", {if(run=="state") " by county" else(" by state")}," with the largest MAE by death rate")

key_group <- mae_hosp %>%
  group_by(pdeath) %>%
  top_n(4, mae) %>%
  mutate(mae = round(mae, 2)) %>%
  {if(run=="state") unite(., "group_mae", name:mae, sep=": ", remove = TRUE) else(unite(., group_mae, !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))}

res_state %>%
  left_join(key_group, by = c(geogroup, "pdeath")) %>%
  filter(!is.na(group_mae)) %>%
  group_by(pdeath,!!as.symbol(geogroup))%>%
  inner_join(truth_dat%>%rename(time=date), by = c("time", geogroup))%>%
  ggplot(aes(x=time, y=currHosp, ymin=currHosp_5pct, ymax=currHosp_95pct)) +
  geom_line(color = "red")+
  geom_ribbon(alpha=.1, fill = "red")+
  geom_point(aes(y=hosp), col="black") +
  facet_wrap(~ pdeath+group_mae, nrow=3)+
  scale_y_sqrt() +
  theme_bw() + 
  theme(legend.position = "bottom") +
  ylab("hosptalizations") +
  theme(axis.text.x = element_text(angle=45,hjust=1)
        )

fig_counter<-fig_counter+1
``` 

`r ifelse(params$hosp_eval, "## Check 4: Compare estimated and reported cases", "## Check 3: Compare estimated and reported cases")`   

```{r lagged_inc_compare, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Estimated and confirmed cases over time by death rate. Cases aggregated by week.")
##Compare to confirmed cases at a national level
usa_sum <-res_state%>%
  inner_join(truth_dat%>%rename(time=date))%>%
  group_by(pdeath, time=lubridate::floor_date(time, unit="week", week_start=1)) %>%
  dplyr::select(starts_with("incidC"), incidI) %>%
  summarize_if(is.numeric, sum)%>%
  group_by(pdeath)%>%
  arrange(time)%>%
  ungroup()%>%
  mutate(pdeath=factor(pdeath, levels=c("high", "med", "low")))%>%
  filter(time!=max(time))

usa_sum%>%ggplot(aes(x=time, y= incidC, ymin= incidC_5pct, ymax= incidC_95pct, linetype=pdeath))+
  geom_line(col = "red ")+
  geom_ribbon(alpha=.1, aes(fill = pdeath)) +
  geom_point(aes(y=incidI), color="black")+
  ylab("approximate cases") + 
  theme(legend.title = element_text("death rate"))+
  theme_bw()

fig_counter<-fig_counter+1

```


```{r mae_infect, fig.height=10, fig.wdith=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Mean absolute error comparing estimated and confirmed cases in", {if(run=="state") " counties" else(" states")}," by death rate")

mae_infect <-res_state %>%
    inner_join(truth_dat%>%rename(time=date)) %>%
    group_by(pdeath, !!as.symbol(geogroup), time=lubridate::floor_date(time, unit="week", week_start=1)) %>%
  {if(run=="state") group_by(.,pdeath, !!as.symbol(geogroup), name, time) else(.)} %>%
    dplyr::select(incidI, starts_with("incidC")) %>%
  summarize_if(is.numeric, sum)%>%
    mutate(error=abs(incidC-incidI), 
           incidC=incidC+1,
           incidI=incidI+1,
           incidC_5pct=incidC_5pct+1,
           incidC_95pct=incidC_95pct+1,
           within = if_else(incidI>incidC_95pct |
                            incidI<incidC_5pct, 0, 1),
           relative = abs(incidC-incidI)/incidI) %>%
  {if(run=="state") group_by(., pdeath, !!as.symbol(geogroup), name) else(.)} %>%
  filter(!is.na(error)) %>%
  summarize(mae = sum(error)/n(),
            relative = sum(relative)/n(),
            within = sum(within)/n())

mae_infect %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=mae, y=group)) +
    geom_col()+
    facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        )+
  xlab("Mean absolute error for infections")+
  scale_x_sqrt()

fig_counter<-fig_counter+1

```

```{r mae_infect_r, fig.height=10, fig.weight=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Relative mean absolute error comparing estimated and confirmed cases", if_else(run=="country", " by state", " by county "))

mae_infect %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=relative, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7))+
    #facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab("Relative mean absolute error for infections (%)") +
  coord_cartesian(xlim = c(0, max((filter(mae_infect, !is.na(relative), relative!=Inf))$relative))) +
  scale_x_continuous(trans = "log1p", breaks = c(0, 0.25, 0.5, 1, 2, 4))


fig_counter <- fig_counter+1

```

```{r within_infect, fig.height=10, fig.wdith=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Proportion of confirmed cases outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval", {if(run=="state") " counties" else(" states")}," by death rate. The dashed line represents the average across counties.")

mae_infect %>%
    {if(run=="state") rename(., group=name) else(rename(.,group=!!as.symbol(geogroup)))} %>%
    ggplot(aes(x=1-within, y=group)) +
    geom_point(aes(col=pdeath), position=position_dodge(0.7))+
    #facet_wrap(~ pdeath)+
    theme_bw() + 
    ylab({if(run=="state") "county" else("state")}) +
    theme(axis.text.x = element_text(angle=45,hjust=1),
        ) +
  xlab(paste0("% of infections outside the ", round((params$pi_hi-params$pi_lo)*100),"% prediction interval")) +
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0, 1.05))+
  geom_vline(xintercept = 1-(mae_infect%>%ungroup()%>%summarize(m=mean(within)))$m, linetype="dashed")

fig_counter<-fig_counter+1

```

```{r key_infect, fig.height=10, fig.wdith=10, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Estimated vs confirmed cases over time in the four", {if(run=="state") " counties" else(" states")}," with the largest MAE by death rate")

key_group <- mae_infect %>%
  group_by(pdeath) %>%
  top_n(4, mae) %>%
  mutate(mae = round(mae, 2)) %>%
  {if(run=="state") unite(., "group_mae", name:mae, sep=": ", remove = TRUE) else(unite(., group_mae, !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))}

res_state %>%
  left_join(key_group, by = c(geogroup, "pdeath")) %>%
  filter(!is.na(group_mae)) %>%
  inner_join(truth_dat%>%rename(time=date))%>%
  group_by(pdeath, group_mae, time=lubridate::floor_date(time, unit="week", week_start=1))%>%
  dplyr::select(incidI, starts_with("incidC")) %>%
  summarize_if(is.numeric, sum)%>%
  group_by(pdeath, group_mae)%>%
  filter(time!=max(time))%>%
  ggplot(aes(x=time, y=incidC, ymin=incidC_5pct, ymax=incidC_95pct))+
  geom_line(color = "red")+
  geom_ribbon(alpha=0.1, fill="red") +
  geom_point(aes(y=incidI), color="black")+
  facet_wrap(~pdeath+group_mae, nrow=3) +
  scale_y_sqrt()+
  theme_bw()+
  theme(legend.position = "bottom")+
  ylab("approximate cases") 
fig_counter<-fig_counter+1

```

## Diagnostics on various model parameters

### Infections to Hospitalization and Deaths

```{r, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Ratio of cumulative deaths to infections by death rate")
# Assumes default pdeath level for config is "high"
res_state%>% 
  mutate(death_inf_ratio = cumDeaths/cumInf)%>%
  ggplot(aes(x=time, y=death_inf_ratio, color=pdeath)) +
    geom_point(alpha=.02) +
    geom_hline(yintercept=config$outcomes$settings[[1]]$incidD$probability$value$value, col="firebrick2")+
  geom_hline(yintercept=config$outcomes$settings[[1]]$incidD$probability$value$value/2, col="seagreen3")+
  geom_hline(yintercept=config$outcomes$settings[[1]]$incidD$probability$value$value/4, col="royalblue3")+
  theme_bw() +
    guides(fill="none") 

fig_counter<-fig_counter+1
```

```{r, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Ratio of cumulative hospitalizations to infections by death rate")

res_state%>% 
  mutate(hosp_inf_ratio = cumHosp/cumInf)%>%
  ggplot(aes(x=time, y=hosp_inf_ratio, color=pdeath)) +
    geom_point(alpha=.02) +
    geom_hline(yintercept=config$outcomes$settings[[1]]$incidH$probability$value$value, col="firebrick2")+
  geom_hline(yintercept=config$outcomes$settings[[1]]$incidH$probability$value$value/2, col="seagreen3")+
  geom_hline(yintercept=config$outcomes$settings[[1]]$incidH$probability$value$value/4, col="royalblue3")+
  theme_bw() +
    guides(fill="none") 

fig_counter<-fig_counter+1
```
### Hospitalizations and Deaths

```{r, death2hosp, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Ratio of cumulative deaths to hospitalizations by death rate")
  
res_state%>% 
  mutate(death_hosp_ratio = cumDeaths/cumHosp)%>%
  ggplot(aes(x=time, y=death_hosp_ratio, color=pdeath)) +
    geom_point(alpha=.015) +
    geom_hline(yintercept=config$outcomes$settings[[1]]$incidD$probability$value$value/config$outcomes$settings[[1]]$incidH$probability$value$value) +
  theme_bw()

fig_counter<-fig_counter+1

```

```{r, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Ratio of lagged, cumulative deaths to hospitalizations by death rate (3-day lag)")

res_state%>% 
  group_by(!!as.symbol(geogroup)) %>% 
  mutate(lead_death=lead(cumDeaths,3)) %>%
  ungroup() %>%
  mutate(death_hosp_ratio = lead_death/cumHosp)%>%
  ggplot(aes(x=time, y=death_hosp_ratio, color=pdeath)) +
    geom_point(alpha=.015) +
    geom_hline(yintercept=config$outcomes$settings[[1]]$incidD$probability$value$value/config$outcomes$setting[[1]]$incidH$probability$value$value)+
  theme_bw()

fig_counter<-fig_counter+1
```


### Appendix. County-level comparisons

```{r, fig.height=70, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Modeled vs reported deaths over time across", {if(run=="state") " counties " else(" states ")} ,"by death rate.")

res_state %>%
  left_join(mae_deaths) %>%
  # {if(run=="state") unite(., "name_mae", name:mae, sep=": ", remove = TRUE) else(unite(., "name_mae", !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))} %>%
  inner_join(truth_dat%>%rename(time=date))%>%
  ggplot(aes(x=time, y=cumDeaths, ymin=cumDeaths_5pct, ymax=cumDeaths_95pct)) +
  geom_line(color = "red")+
  geom_ribbon(alpha=.1, fill = "red")+
  geom_point(aes(y=Deaths), col="black") +
  facet_grid({if(run=="state") name else(USPS)} ~ pdeath, scales = "free")+
  #geom_text(data = label, label = "mae") +
  #scale_y_sqrt() +
  theme_bw() + 
  theme(legend.position = "bottom") +
  ylab("deaths") +
  theme(axis.text.x = element_text(angle=45,hjust=1))

fig_counter<-fig_counter+1
```

```{r, fig.height=70, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Estimated vs confirmed incident deaths over time across", {if(run=="state") " counties " else(" states ")} ,"by death rate (aggregated by week).")

res_state %>%
  left_join(mae_infect) %>%
   # {if(run=="state") unite(., "name_mae", name:mae, sep=": ", remove = TRUE) else(unite(., "name_mae", !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))} %>%
  inner_join(truth_dat%>%rename(time=date))%>%
{if(run=="state") group_by(.,pdeath, time=lubridate::floor_date(time, unit="week", week_start=1), group=name) else(group_by(.,pdeath, time=lubridate::floor_date(time, unit="week", week_start=1), group=USPS))}%>%
  dplyr::select(starts_with("incidD")) %>%
  summarize_if(is.numeric, sum)%>%
  group_by(pdeath, group) %>%
  filter(time!=max(time))%>%
  ggplot(aes(x=time, y=incidD, ymin=incidD_5pct, ymax=incidD_95pct))+
  geom_line(color= "red")+
  geom_ribbon(alpha=0.1, fill="red") +
  geom_point(aes(y=incidDeath), color="black")+
  facet_grid(group ~ pdeath, scales = "free")+
  #scale_y_sqrt()+
  theme_bw()+
  theme(legend.position = "bottom")+
  ylab("incident deaths") 

fig_counter<-fig_counter+1
```

```{r, fig.height=70, fig.cap=cap, eval=params$hosp_eval}
cap<-paste0("**Fig.", fig_counter, "**: Estimated vs confirmed occupied hospital beds over time across", {if(run=="state") " counties " else(" states ")} ,"by death rate.")

res_state %>%
  left_join(mae_hosp) %>%
   # {if(run=="state") unite(., "name_mae", name:mae, sep=": ", remove = TRUE) else(unite(., "name_mae", !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))} %>%
  inner_join(truth_dat%>%rename(time=date))%>%
  {if(run=="state") group_by(., pdeath, name) else(group_by(., pdeath, USPS))} %>%
  filter(time!=max(time))%>%
  ggplot(aes(x=time, y=currHosp, ymin=currHosp_5pct, ymax=currHosp_95pct))+
  geom_line(color= "red")+
  geom_ribbon(alpha=0.1, fill="red") +
  geom_point(aes(y=hosp), color="black")+
  facet_grid({if(run=="state") name else(USPS)} ~ pdeath, scales = "free")+
  #scale_y_sqrt()+
  theme_bw()+
  theme(legend.position = "bottom")+
  ylab("occupied hospital beds") 

fig_counter<-fig_counter+1
```

```{r, fig.height=70, fig.cap=cap}
cap<-paste0("**Fig.", fig_counter, "**: Estimated vs confirmed cases over time across", {if(run=="state") " counties " else(" states ")} ,"by death rate (aggregated by week).")

res_state %>%
  left_join(mae_infect) %>%
   # {if(run=="state") unite(., "name_mae", name:mae, sep=": ", remove = TRUE) else(unite(., "name_mae", !!as.symbol(geogroup):mae, sep=": ", remove = FALSE))} %>%
  inner_join(truth_dat%>%rename(time=date))%>%
{if(run=="state") group_by(.,pdeath, time=lubridate::floor_date(time, unit="week", week_start=1), group=name) else(group_by(.,pdeath, time=lubridate::floor_date(time, unit="week", week_start=1), group=USPS))}%>%
  dplyr::select(incidI, starts_with("incidC")) %>%
  summarize_if(is.numeric, sum)%>%
  group_by(pdeath, group)%>%
  filter(time!=max(time))%>%
  ggplot(aes(x=time, y=incidC, ymin=incidC_5pct, ymax=incidC_95pct))+
  geom_line(color= "red")+
  geom_ribbon(alpha=0.1, fill="red") +
  geom_point(aes(y=incidI), color="black")+
  facet_grid(group~ pdeath, scales = "free")+
  #scale_y_sqrt()+
  theme_bw()+
  theme(legend.position = "bottom")+
  ylab("cases") 

```